Designing Turk Experiments for Visual Statistical Inference

### 2013-06-18 paper_turk.tex
plan for a turk task

Human observers are needed to evaluate lineups that are used to test the significance of findings using statistical graphics. One good option is to recruit people from online workplace like Amazon Mechanical Turk (MTurk). It has the facilities to create online task that would allow people to evaluate lineups and get paid. MTurk is designed for simple and easy tasks. The technical design of the underlying experiment for visual inference may be complex and the tools available to design this from MTurk is just too simple. In this paper we describe how to design MTurk experiments, present an alternative way to conduct the survey on lineups by designing a separate web application and getting turk worker do their job from this web site. The web site is now hosted on the Iowa State University public domain and has been in use for multiple experiments \citep{majumder:turk}. It turns out to be a very efficient way of getting lineups evaluated by online observers. Getting results from this web site is very convenient and secure.

@@

The power of visual test is studied by \cite{majumder:2013} and it is revealed that power could be as good as conventional test and in some scenarios even better. But where the conventional test does not exists, visual inference could be the only inferential procedure without compromising a lot in power.

These developments open up a whole new area of statistical research where lineups need to be evaluated by human observer. There are some reasons a researcher needs to evaluate lineups. One is to assess the power of the visual test \citep{heike:2012} for different visual test statistics. The another reason would be to make decision based on the lineup, i.e., to use lineup protocol in practical application \citep{niladri:2012}. Other reasons could be to present the results of the conventional test with visual tools such as lineup.

@@

MTurk will provide workers who are used to doing simple task. Thus, for lineups to be evaluated a simple task needs to be created through MTurk. But People who need to make statistical decision based on lineup will need a system that can provide an easy solution to this challenge.  This paper provides a complete solution to this. This paper is organized the way a researcher may work with lineup and like to get feedback data from the observer. Section \ref{sec:turk_exp} presents the details description of an experiment with lineups and things to consider before a turk task. Section \ref{sec:web_application} presents the design of an web application to get lineups evaluated with additional flexibilities and options that may not possible through MTurk. Section \ref{sec:turk_task} describes how to create an MTurk task, mange workers and process payments. Finally Section \ref{sec:turk_data} presents some data obtained from various experiments done through the web application and discusses about the quality of the data.

@@

\subsection{Sample size estimation} For a given proportion $p$ we want to have margin of error (ME) to be 0.1. Thus we have $$ME =1.96 \sqrt{ \frac 1 n p(1-p)} \le 0.05$$ which gives us the estimation of minimum sample size $$n \geq \frac{p(1-p)}{(0.05/1.96)^2}.$$ Now from the theoretical power curve for each parameter combinations shown in table \ref{tbl:experiment_params} we know the power(say $p$) and thus we can estimate the sample size required for that specific combinations of parameter. We collect data such that each of the parameter combinations in the table \ref{tbl:experiment_params} has approximately the estimated sample size that we calculated here.

@@

\subsection{Planing the Turk Task}
Question to ask

Whether reasoning would be collected or not

Multiple or single response

Test plot added or not

Training needed or not

Feedback given after every evaluation or not

How many lineups to show

Are the lineups randomly selected?

@@

The information collected from each individual is shown in Table \ref{tbl:data_info}. Data received from each individual are automatically saved in a secured mysql server maintained by the department of statistics, Iowa state university.

@@

Turk workers are usually small payee workers. There several issues related to the payment of their effort. These are briefly discussed in the following section and we intend to work more on this as we progress through this dissertation work.

\subsection{Creating Task for Lineup Evaluation} Task description, number of people to recruit, time allowed to finish the task, specify the qualification needed, setting the duration of the task, offering the pay per task.

\subsection{Accepting or Rejecting the Task} In our design we keep a test lineup plot which is very easy to evaluate. The general criteria may be to reject payment when workers do not get that easy test lineup plot. Our experience suggest that there are workers who did not get that test plot but their overall success rate is very high. So depending on only one criteria the payment should not be made. These issues would be addressed in our future work based on the several turk experiments that we intend to carry out.

\subsection{Processing Payment}Amazon Mechanical Turk suggest that each worker gets \$6/hour as wage. Thus we need to estimate how much time a tusk may take to complete and based on that we have to specify the payment for each task. Our experience indicates that a better payment lures more serious workers who usually provide cleaner data which is more reliable. We may study this issue while we do multiple turk experiments.

\subsection{Managing Worker} pay bonus, appreciate worker by sending email, block worker etc.

@@

\subsection{Selection Bias} Since data are collected through web interface it is possible to have the selection bias in the turk experiment we did. In this section we intend to analyze to what extent this selection bias has occurred and how we can adjust for this.

@@

\section{Conclusion} This paper presents a complete solution to the problem of designing a simulation experiment for lineup and recruiting people to get the lineups evaluated. The online application design provides flexibility to control how the multiple lineups would be presented to an observer. Scalable Vector Graphics (SVG) are used for lineup so that observer can click on the lineup to pick certain plot. This also made the multiple plot selection from a lineup easier and convenient. Multiple online experiments are done using this web application and result suggests that the application worked as planned.

One of the main features of the web application is that it produces simple task for the worker who are used to doing so from MTurk but still provides many flexibilities to the researcher who need lineups to be evaluated as per complex experimental requirement. The design of this application allows recruiting people from any source not necessarily just from MTurk. The web application is now hosted on Iowa State University public domain \citep{majumder:turk} and any number of experiments can be done through this web site without changing the core of this application.

The next direction of this work is to make a complete package so that anyone can reproduce this web application, customize according to their need and run the MTurk experiments as part of their research that involves lineups. This would save lot of time which researcher can use focusing on their actual research. This will also help lineup protocol to be used frequently since it will provide an ease of its use in making inferential decisions.

>>>>

Human observers are needed to evaluate lineups that are used to test the significance of findings using statistical graphics. One good option is to recruit people from online workplace like Amazon Mechanical Turk (MTurk). It provides features to create online task that allow people to evaluate lineups and get paid. MTurk is designed for simple and easy tasks. The technical design of the underlying experiment for lineup evaluation may be complex and the tools available to design this from MTurk is just too simple. In this paper we present the design of MTurk experiments for lineup evaluation, provide an alternative way to conduct the survey on lineups by developing a separate web application and getting turk worker do their job from that web site. The web site is now hosted on the Iowa State University public domain and has been in use for multiple experiments \citep{majumder:turk}. It turns out to be a very efficient way of getting lineups evaluated by online observers. Getting results from this web site is very convenient and secure.

{\bf Keywords: \sf statistical graphics, lineup, Amazon Mechanical Turk, visual inference, visualization, Crowdsourcing, Human Intelligence.}

@@

\cite{majumder:2013}  further developed visual inference by refining the terminologies and providing the methods of obtaining the power. it is revealed that visual test power can be as good as the best available conventional test and in some scenarios even better. This work establishes the validity of lineup protocol to be used as a tool for statistical testing. In the situations where no conventional test exists, visual inference can be the only inferential procedure without compromising a lot in power because of its non-parametric nature and few assumptions.

These developments open up a whole new area of statistical research where lineups need to be evaluated by human observer. For small scale or day to day research it is possible to have people around to get the lineups evaluated. But sometimes it is needed to have many observers to evaluate lineups. For example, to assess the power of the visual test for different visual test statistics \cite{heike:2012} recruited human observers to evaluate lineups.   \cite{niladri:2012} used lineup protocol in practical applications. Other reasons to evaluate lineups are to present the results of the conventional test with visual tools such as lineup.

@@

MTurk will provide workers who are used to doing simple task. Thus, for lineups to be evaluated a simple task needs to be created through MTurk. But People who need to make statistical decision based on lineup will need a system that can provide an easy solution to this challenge.  This paper provides a complete solution to this. This paper is organized the way a researcher may work with lineup and like to get feedback data from the observer. Section \ref{sec:turk_exp} presents the details description of an experiment with lineups and things to consider before a turk task. Section \ref{sec:web_application} presents the design of an web application to get lineups evaluated with additional flexibilities and options that may not be possible through MTurk. Section \ref{sec:turk_task} describes how to create an MTurk task, mange workers and process payments. Finally Section \ref{sec:turk_data} presents some data obtained from various experiments done through the web application and discusses about the quality of the data.

@@

\subsection{Sample size estimation} By sample size we mean the number of evaluations per lineup. It is different than number of people who evaluates lineup. If multiple lineups are evaluated by a person, sample size will be larger than number of people recruited from MTurk.

To have an idea how many evaluations are required for a lineup one approach can be to have a prior idea of proportion correct for the lineup. For a given proportion $p$ we want to have margin of error (ME) to be 0.1. Thus we have $$ME =1.96 \sqrt{ \frac 1 n p(1-p)} \le 0.05$$ which gives us the estimation of minimum sample size $$n \geq \frac{p(1-p)}{(0.05/1.96)^2}.$$

%Now from the theoretical power curve for each parameter combinations shown in table \ref{tbl:experiment_params} we know the power(say $p$) and thus we can estimate the sample size required for that specific combinations of parameter. We collect data such that each of the parameter combinations in the table \ref{tbl:experiment_params} has approximately the estimated sample size that we calculated here.

@@

\subsection{Plan for a Turk Task} \label{sec:task_plan} To make a good use of MTurk crowd source, it is important to split any big project into small pieces or Task. To present each task for the workers to do, a Human Intelligence Task or HIT needs to be designed which includes crisp and clear instructions of the task, descriptions of specific input and output desired and payment information. To design a HIT for lineups to be evaluated we need to consider the following issues.

\begin{itemize}

\item {\bf IRB approval:} Since this is a human subject experiment proper approval has to be taken from Institutional Review Board or IRB. This approval includes how the task will be performed, how the anonymity of the subjects will be maintained etc. For this we plan to have a consent form which the MTurk workers have to agree before participating the experiment. The consent form is approved by IRB.

\item {\bf Lineup question:} Each lineup should be presented with a question that the worker has to answer. The question needs to be clear and technical word should be removed as the MTurk workers may not be aware of those terms. The question is important for lineups as well. Very common question to evaluate a lineup is ``Which plot is the most different?". But for complicated studies the question may be quite different \citep{majumder:socio}.

\item {\bf Data input:} For lineup experiments data input means mainly the lineups that are going to be presented for evaluations. Lineups may be presented in some sequence or completely at random. We need to decide whether a test lineup will be included or not in the pool of lineups going to be presented. Some other inputs may accompany with each lineup. Those include lineup question, how many lineups to be evaluated by the worker etc. Anything that the worker will see changing with each lineup is considered as data input to the worker. For different experimental needs this input may be different. For example, one may decide to let the worker know if each evaluation made is correct or wrong right after the feedback. This is an input for the worker.

\item {\bf Data output:} This means the data collected from the MTurk workers. That includes mainly the response on lineup question. Single or multiple responses can be requested for each lineup. Other optional data that may be collected are as follows;

\begin{enumerate}
\item Demographic information of the observer
\item Reasons for choice
\item Confidence levels of the response provided
\item Location information
\item Time of the evaluation
\end{enumerate}

\item {\bf Payment:} Payment plays an important role on data quality and how fast the data can be collected. It depends on how many lineups are being evaluated by a worker, how much time it may require to finish the task or how hard the task is in general.

%Whether reasoning would be collected or not
%
%Multiple or single response
%
%Test plot added or not
%
%Training needed or not
%
%Feedback given after every evaluation or not
%
%How many lineups to show
%
%Are the lineups randomly selected?

\end{itemize}

@@

The default information that the system is designed to collect from each individual is shown in Table \ref{tbl:data_info}. Data received from each individual will be automatically saved in a secured mysql server.

@@

Turk workers are usually small payee workers. There are several issues related to the payment of their effort. These are briefly discussed in the following section.

% and we intend to work more on this as we progress through this dissertation work.

\subsection{Creating Task for Lineup Evaluation} Task description, number of people to recruit, time allowed to finish the task, specify the qualification needed, setting the duration of the task, offering the pay per task. The task needs to be created as per the task plan described in Section \ref{sec:task_plan}.

\subsection{Accepting or Rejecting the Task} As per design we keep a test lineup plot which is very easy to evaluate. The general rule may be to reject payment when workers do not get that easy test lineup plot. Our experience suggests that there are workers who do not get that test plot but their overall success rate is very high. So depending on only one criteria the payment should not be made.

%These issues would be addressed in our future work based on the several turk experiments that we intend to carry out.

\subsection{Payment for the Worker}Amazon Mechanical Turk suggests that each worker gets \$6/hour as wage. Thus we need to estimate how much time a task may take to complete and based on that we have to specify the payment for each task. Our experience indicates that a better payment brings more serious workers who usually provide cleaner data which is more reliable.

%We may study this issue while we do multiple turk experiments.

\subsection{Managing Worker} Pay bonus, appreciate worker by sending email, block worker etc.

@@

\subsection{Selection Bias}

%Since data are collected through web interface it is possible to have the selection bias in the turk experiment we did. In this section we intend to analyze to what extent this selection bias has occurred and how we can adjust for this.

@@

\section{Conclusion} This paper presents a complete solution to the problem of designing a simulation experiment for lineup and recruiting people to get the lineups evaluated. The online application design provides features to control how the multiple lineups can be presented to an observer. Scalable Vector Graphics (SVG) are used for lineup so that observer can click on the lineup to pick certain plot. This also made the multiple plot selection from a lineup easier and convenient. Multiple online experiments are done using this web application and result suggests that the application worked as planned.

One of the main features of the web application is that it produces simple task for the worker but still retains many flexibilities to the researcher who need lineups to be evaluated as per complex experimental requirement. The design of this application allows recruiting people from any source not necessarily just from MTurk. The web application is now hosted on Iowa State University public domain \citep{majumder:turk} and any number of experiments can be done through this web site without changing the core of this application.

The next direction of this work is to make a complete package so that anyone can reproduce this web application, customize according to their need and run the MTurk experiments as part of their research that involves lineups. This will also help lineup protocol to be used frequently since it will provide an ease of its use in making inferential decisions.
